\section{Moduli Space of Unitary Connections on a Riemann Surface}
\label{s:vectorbundles}
	The moduli space $\MM$ which we are interested in studying has three equivalent descriptions, thanks to the work of Narasimhan and Seshadri and Donaldson. The simplest to state is that for a compact oriented Riemann surface $\Sigma$ and unitary group $G$, $\MM$ is the GIT quotient $\Hom(\pi_1(\Sigma), G)\sslash G$. Namely, $\MM$ is the equivalence classes of representation of $\pi_1(\Sigma)$ into $G$. Another description is as the set of unitary connections on the trivial principal $G$ bundle $P$ over $\Sigma$, which makes the symplectic structure clear. The third description is as the space of complex structures on a smooth vector bundle $E$, which brings the complex behaviour into focus.
	
	In brief, the relationship between the pictures is as follows. Given a representation of $\pi_1(\Sigma)$ to $G$, one obtains a unitary connection by thinking of the representation as a map of principal bundles $\pi_1(\Sigma)\times \Sigma \to P = G\times \Sigma$, (elab required)
	
	Given a unitary connection, the holonomy of the connection gives a representation of $\pi_1(\Sigma)$ into $G$, and the $(0,1)$ part of the connection form gives a holomorphic structure for the vector bundle. 
	\subsection{Symplectic Picture}
	 Let $\Sigma$ be the compact connected Riemann surface of genus $g$. Consider the trivial principal $G=SU(2)$ bundle $P$, over $\Sigma$ and let $\cA$ denote the space of smooth prinicpal connections on $P$. In a fixed trivialization $P \cong G\times \Sigma$, a connection is determined by a form $A \in \Omega^1(\Sigma)\otimes \mathfrak{g}$. If we let $\cA_0$ denote the subspace of flat connections $(0 = F:=dA + A\wedge A)$, we can identify
	\begin{equation}
	\cA_0 = \{A \in \Omega^1(\Sigma)\otimes\mathfrak{g} (=\cA) ~|~ dA + A\wedge A = 0\}.
	\end{equation}
	Then the gauge group, $\cG = \Hom(\Sigma, G)$ acts on $\cA$ as follows: for $g\in \cG$,
	\begin{equation}
	g\circlearrowright A := g^{-1}Ag + g^{-1}dg.
	\end{equation}
	The vector space $\cA$ has a natural symplectic structure, which comes from the inner product (the Killing form) on the Lie Algebra $\mathfrak{g}$, $K:\mathfrak{g}\otimes\mathfrak{g}\to\mathbb{C}$. If $A = \alpha \otimes X$ and $B = \beta \otimes Y$ then we can define
	\begin{equation}
	\omega(A,B) = \int\limits_\Sigma K(X,Y)\alpha\wedge \beta.
	\end{equation}
	This symplectic stucture is preserved by the action of $\cG$; we have
	\begin{align*}
	(g^{-1} A g + g^{-1}dg) \wedge (g^{-1} B g + g^{-1}dg) &= g^{-1}A\wedge B g + g^{-1}(dg\wedge Bg) + g^{-1}A\wedge dg + g^{-1}dg \wedge g^{-1}dg \\
	&= g^{-1} A\wedge B g + g^{-1}(d(gB) + d(Ag)g^{-1} - dA - gdB)g
	\end{align*}
	
	Importantly, the curvature $F = dA + A\wedge A$ is actually a moment map for the action of $\cG$ (also to be shown here). This lets us acquire the moduli space of flat connections by symplectic reduction:
	\begin{equation}
	\MM = \cA\sslash\cG = F^{-1}(0)/ \cG= \cA_0/ \cG.
	\end{equation} 
	Symplectic reduction also gives us a symplectic structure on the quotient space $\MM$, such that under the pullback by the quotient map, $q:\cA_0 \to \MM$, we recover the symplectic form $\omega$ for $\cA$.


	\subsection{Complex Picture}
	There is another picture of this moduli space, thanks to Narasimhan and Seshadri, as well as by Donaldson. Fix a smooth complex vector bundle $E$ over $\Sigma$, of rank $n$ and degree $k$. We are interested in the space of possible holomorphic structures we can put on $E$.
	\begin{definition}
		A \textit{holomorphic structure} on a complex vector bundle $E$ is a choice of trivializations $\{U_\alpha, \phi_\alpha\}$ for $E$, such that the transition functions
		\begin{equation*}
			T_{\alpha,\beta} = \phi_\alpha \circ \phi^{-1}_\beta: E|_{U_\alpha \cap U_\beta} \to E|_{U_\alpha \cap U_\beta},
		\end{equation*}
		are biholomorphic. 
	\end{definition}
	 An equivalent and convenient characterization is as follows. Given a holomorphic structure, in every chart $\{U_\alpha\}$, with local frame $\{e_1,...,e_n\}$ for $E$, we can define a local operator taking a section $s = s^i e_i$ to
	\begin{equation*}
		\dbar_E(s) = \dbar(s^i)\otimes e_i,
	\end{equation*}
	where $\dbar$ is the usual Cauchy-Riemann operator on $\mathbb{C}$. Now, let us check this operator is well defined globally on $E$. On the intersection $U_\alpha \cap U_\beta$, with local frames $\{e_i\}$ and $\{f_i\}$, we have $s = s^i e_i = \tilde{s}^i f_i$, with $s^i = {T_{\alpha\beta}}^i_j\tilde{s}^j.$ Since $T_{\alpha\beta}$ is biholomorphic, we have:
	\begin{align*}
		\dbar_E(s) = \dbar(s^i)\otimes e_i &= \dbar({T_{\alpha\beta}}^i_j \tilde{s}^j)\otimes f_i\\
		&= {T_{\alpha\beta}}^i_j \dbar(\tilde{s}^j)\otimes f_i.
	\end{align*}
	Hence $\dbar_E$ transforms with $T_{\alpha\beta}$ and it is globally well defined. We call $\dbar_E$ the \textit{Dolbeault Operator} corresponding to the holomorphic structure on $E$. Conversely, if we have a differential operator $\dbar_E:\Gamma(E) \to \Omega^{0,1}(\Sigma)\otimes \Gamma(E)$, we can define a holomorphic structure on $E$. (pf or citation needed)
	
	Therefore, in order to study the space of holomorphic structures on $E$, we can equivalently study the space of Dolbeault operators on $E$. In a smooth local trivialization of $E$, we can write 
	\begin{equation*}
		\dbar_E = \dbar + B,
	\end{equation*}
	where $\dbar$ is the usual Cauchy-Riemann operator and $B \in \Omega^{0,1}(M, \End(E))$. Since $\dim \Sigma = 1$ there is no constraints on $B$ (citation needed) and so our space is an affine complex space with translations $\Omega^{0,1}(M,\End(E))$. We have an action of $\text{Aut}(E)$ on this space by change of basis, whose orbits are (by definition of Aut) isomorphism classes of holomorphic bundles $E$ of rank $n$ and degree $k$, and it is the space of these orbits, $N(n,k)$, that we wish to describe. 
	
	However, in order to get a well-behaved moduli space, we must introduce a condition called stability. 
	\begin{definition}
		Let the \emph{slope} of a bundle $E$ be
		$$\mu := c_1(E)/\text{rank}(E),$$
		where $c_1(E)$ denotes the first Chern class. Then $E$ is said to be \textit{stable} if, for every proper subbundle $F$ of $E$, $\mu(F) < \mu(E)$. If the inequality is not strict, $E$ is \textit{semi-stable}.
	\end{definition}
	Stability is required to guarantee that once we quotient our space by $\text{Aut}(E)$, we end up with a space that is Hausdorff (Mumford,Fogarty GIT book). To motivate this claim, let us give an example of two isomorphism classes of holomorphic bundle which intersect at an unstable bundle. Let $\Sigma = \mathbb{P}^1$ and $E = \OO(1)\oplus \OO(-1)$. Then
	\begin{equation}
		c_1(E) = c_1(\OO(1))c_1(\OO(-1)) = -1,
	\end{equation} 
	therefore $\mu(E) = -1/2$. However $\OO(1)$ is a proper subbundle of $E$ and $\mu(\OO(1)) = 1$, so $E$ is unstable. Letting $U_0 = \mathbb{P}^1 - \{\infty\}$ and $U_1 = \mathbb{P}^1 - \{0\}$, $E$ has transition function $T$ on $U_0 \cap U_1$ given by
	\begin{equation*}
	T(z) = \begin{bmatrix}
	z & 0\\
	0 & \frac{1}{z}
	\end{bmatrix}, z \neq 0, z\neq \infty.
	\end{equation*}
	Now consider conjugating $E$ by the following family in $Aut(E)$
	\begin{align*}
		\begin{bmatrix}
		1 & b\\
		c & 1\\
		\end{bmatrix}
		\begin{bmatrix}
		z & 0\\
		0 & \frac{1}{z}\\
		\end{bmatrix}
		\begin{bmatrix}
		1 & -c\\
		-b & 1\\
		\end{bmatrix} = \begin{bmatrix}
		z - \frac{b^2}{z} & \frac{b}{z}-cz\\
		cz - \frac{b}{z} & \frac{1}{z}-c^2 z\\
		\end{bmatrix}.
	\end{align*}
	If we let $c=0$ and $b=t$ we get a family $F(t)$ of vector bundles with transition matrices
	\begin{equation*}
		T_{F}(t) = \begin{bmatrix}
		z-t^2/z & t/z\\
		-t/z & 1/z
		\end{bmatrix},
	\end{equation*}
	and if we let $c=t$ and $b=0$ we get a family $G(t)$ of vector bundles with transition matrices
	\begin{equation*}
		T_{G}(t) = \begin{bmatrix}
		z & -tz\\
		tz & \frac{1}{z}-t^2 z
		\end{bmatrix}.
	\end{equation*}
	As $t\to 0$, both $F(t)$ and $G(t)$ go to $E$. Therefore, $E$ is in the orbit of both $F(1)$ and $G(1)$ under the action of Aut$(E)$. This means any open set containing $[F(1)]$ must contain $E$, and any open set containing $[G(1)]$ must contain $E$, and therefore these two points serve as a counterexample to Hausdorffness.
	
	For this reason, we will restrict our attention to only the subset of $N(n,k)$ consisting of semi-stable bundles. In particular, we will denote the space of degree $0$ semi-stable bundles as $\MM$. 
	
	
	
	Since stability is an open condition, we are safe to consider deformations. At a bundle $(E,\dbar_E)$ with holomorphic structure given by transition functions $T_{\alpha,\beta}$, we can consider deforming the holomorphic structure to 
	\begin{equation}
		T_{\alpha,\beta}(\epsilon) = T_{\alpha,\beta} + \epsilon t_{\alpha,\beta},
	\end{equation}
	where $t_{\alpha,\beta} \in \Omega^{0,1}(M,\End(E))$ and $\epsilon^2=0$. For this to remain a well-defined holomorphic structure, we require that $T_{\alpha,\beta}(\epsilon)$ satisfies the cocycle condition for all $\epsilon$. That is, on $U_{\alpha}\cap U_{\beta}\cap U_{\gamma}$,
	\begin{align*}
		T_{\alpha,\beta}(\epsilon)T_{\beta,\gamma}(\epsilon) &= T_{\alpha,\gamma}(\epsilon)\\
		\left(T_{\alpha,\beta} + \epsilon t_{\alpha,\beta} \right)
		\left(T_{\beta,\gamma} + \epsilon t_{\beta,\gamma} \right) &=
		\left(T_{\alpha,\gamma} + \epsilon t_{\alpha,\gamma} \right)\\
		T_{\alpha,\beta}T_{\beta,\gamma} + \epsilon(t_{\alpha,\beta}T_{\beta,\gamma} + T_{\alpha,\beta} t_{\beta,\gamma}) + \epsilon^2 t_{\alpha,\beta}t_{\beta,\gamma} &= T_{\alpha,\gamma} + \epsilon t_{\alpha,\gamma}
	\end{align*}
	using that $\epsilon^2 = 0$ and $T_{\alpha,\beta}$ satisfy the cocycle condition, we have
	\begin{align*}
		T_{\alpha,\gamma} + \epsilon(t_{\alpha,\beta} T_{\beta,\gamma} + T_{\alpha,\beta} t_{\beta,\gamma}) &= T_{\alpha,\gamma} + \epsilon t_{\alpha,\gamma}\\
		t_{\alpha,\beta} T_{\beta,\gamma} + T_{\alpha,\beta} t_{\beta,\gamma} &= t_{\alpha,\gamma}.
	\end{align*}
	This condition tells us that $t_{\alpha,\beta}$ is a 1 cocycle in the sheaf $\End(E)$. When we quotient the action of of $\text{Aut}(E)$, we find that the tangent space to $N(n,k)$ is $H^1(\End(E))$. 
	
	When $E$ has a hermitian metric $h:E\otimes E \to \C$, the conjugate Hodge star $\bar{\star}:\Omega^{0,1}(\Sigma) \to \Omega^{1,0}(\Sigma)$ combined with $h$ allows us to define a hermitian inner product on $H^1(\End (E))$.  First $h$ defines a metric on $\End E$; if $A,B\in \End E$, let
	\begin{equation}
		g(A,B) = \Tr(A^\dagger B),
	\end{equation}
	where $\dagger$ is defined in terms of $h$, by $h(Ae,e) = h(e,A^\dagger e)$ for all $e\in E$. Then for any $\alpha = A \otimes a$, $A\in \End E$ and $a \in \Omega^{0,1}(\Sigma)$, we define:
	\begin{align}
		\bar{\ast}_E \alpha = g(A,-)\otimes \bar{\ast}a, 
	\end{align}
	and
	\begin{equation}
		\langle \alpha, \beta \rangle = \int\limits_\Sigma \alpha \wedge_g \bar{\ast}_E \beta =\int\limits_\Sigma g(A,B)~a\wedge \bar{\ast} b.
	\end{equation}
	This is just another form of Serre Duality (citation). In a local co-ordinate chart where $\alpha = Adz$ and $\beta = Bdz$, this takes the form
	\begin{equation}
		\langle \alpha, \beta \rangle = \int\limits_\Sigma \Tr(A^\dagger B)~dz\wedge d\bar{z}.
	\end{equation}
The relationship between this space of connections and the space of holomorphic vector bundles is described by the Narasimhan-Seshadri theorem. In one direction, given a flat connection $A$ on $P$, inducing a connection on the associated bundle $E$, we can decompose $A = A^{0,1} + A^{1,0}$. This allows us to take $\dbar_E = A^{0,1}$ as a complex structure on $E$ corresponding to the flat connection $A$. The Narasimhan-Seshadri theorem guarantees that this structure will define a stable bundle, and also gives the converse direction; that flat stable structures $\dbar_E$ define flat unitary connections $A$. 
